A framework for adaptive width control of dense contour-parallel toolpaths in additive manufacturing

### 2019-08-29 4_method.tex
Tim: remove upper half of beadings B which was unused and fix some fomulae issues

\subsection{Beading}\label{sec_peripheral_height_adjustment}
Now that we have determined the bead counts in the central regions we will describe how the peripheral regions are handled.
Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
while that would suffice for the evenly distributed beading scheme, it wouldn't allow for more sophisticated, non-linear schemes (see \cref{peripheral_heights}).
Instead we determine the radial distance to the boundary at which each bead should occur.
Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, startign from the outer bead and ending in the center.
Together with a sequence of bead widths $W$ these form what we call a \emph{beading} $B$.
For our distributed beading scheme we compute the beading for a central node $v$ with $n = \hat{b}_v$ beads and a diameter $d = 2R(v)$  as:
\begin{align*}
    B(n,d) &= \left( W(n,d), L(n,d) \right)   &=   \left( \left\{  w_0 , \dots, w_{n-1} \right\}, \left\{ l_0 , \dots, l_{n-1} \right\} \right) \\
    w_i &= 2R(v) / n  & \text{for all $i < n$}\\
    l_i &= 2R(v) / n (i + \nicefrac12) & \text{for all $i < n$}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
An example beading is visualized in the top of \cref{beading_interpolation}:
$B^V$ cover the total horizontal distance $d$ using $n=4$ beads all with the same width and radial locations $l$ evenly divided over the length $d$.

@@

\paragraph{Beading interpolation}
The beading is defined in terms of an integer number of beads, while we have assigned a fractional bead count to nodes within a transition region.
In order to generate a beading for a node $v$ with $n < b^*_v < n+1 $ we linearly interpolate the bead width and location of the first and last $n/2$ lines between a beading $B^V$ based on $n$ and a beading $B^W$ based on $n+1$ (see \cref{beading_interpolation}).
Such interpolation is also used to deal with beading conflicts (see \cref{beading_conflict_problem}).
We therefore also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node.

@@

\begin{figure}
\centering
\includegraphics[width=.8\columnwidth]{sources/method/beading_interpolation_v2.pdf}
\caption{
Interpolation between two beadings $B^V$ and $B^W$ with a ratio $x$ results in a beading $B^x$.
Distances between the thick black lines constitute diameters $d$,
the toolpath locations are visualized as dots,
the widths are visualized as bidirectional arrows
and the middle is highlighted in red.
}
\label{beading_interpolation}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings to generate sites along trapezoids.
\subref{trapezoid_beading_beading} shows half of the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective sites along the support edges.
No sites will be generated along marked edges.
Wide black lines are outline segments, marked nodes and edges in blue, the sites in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
}
\label{site_placement}
\end{figure}

>>>>

\subsection{Beading}\label{sec_peripheral_height_adjustment}
Now that we have determined the bead counts in the central regions we will describe how the peripheral regions are handled.
Determining bead count values for the unmarked nodes and interpolating linearly along the unmarked edges would mean that toolpath sites would be distributed evenly along each unmarked bone;
while that would suffice for the evenly distributed beading scheme, it wouldn't allow for more sophisticated, non-linear schemes (see \cref{peripheral_heights}).
Instead we determine the radial distance to the boundary at which each bead should occur.
Each central node is associated with a sequence of radial distances $L$ which control the locations of the beads, starting from the outer bead and ending in the center.
Together with a sequence of bead widths $W$ these form what we call a \emph{beading} $B$.
For our distributed beading scheme we compute the beading for a central node $v$ with $n = \lfloor \hat{b}_v \rfloor$ beads and a diameter $r = R(v)$  as:
\begin{align*}
    B(n,r) &= \left( W(n,r), L(n,r) \right)   &=   \left( \left\{  w_0 , \dots, w_{\lceil n/2 \rceil-1} \right\}, \left\{ l_0 , \dots, l_{\lceil n/2 \rceil-1} \right\} \right) \\
    w_i &= r / n  & \text{for all $i \in \mathbb{N} : i < n / 2 $}\\
    l_i &= r / n (i + \nicefrac12) & \text{for all $i \in \mathbb{N} : i < n / 2 $}
\end{align*}
where
$w_i$ and $l_i$ are the width and location of the $i$th bead,
respectively, counting from the outline inward.
Example beadings for an odd and even bead count with arbitrary widths are visualized in \cref{example_beading}.

@@

\paragraph{Beading interpolation}
The beading is defined in terms of an integer number of beads, while we have assigned a fractional bead count to nodes within a transition region.
In order to generate a beading for a node $v$ with $n < b^*_v < n+1 $ we linearly interpolate the bead widths and locations between a beading $B^1$ based on $n$ and a beading $B^2$ based on $n+1$ (see \cref{beading_interpolation}).
Such interpolation is also used to deal with beading conflicts (see \cref{beading_conflict_problem}).
There we also apply beading interpolation from a marked node $v_m$ upward along unmarked bones,
and interpolate between $v_m$ and the beading at the top of the slope over some distance $t_\text{beading}$ from the lower marked node.

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation_beading.pdf}
\caption{Example beadings}\label{example_beading}
\end{subfigure}
\begin{subfigure}{0.4\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_interpolation.pdf}
\caption{Interpolation}
\end{subfigure}
\caption{
Interpolation between two beadings $B^1$ and $B^2$ with odd and even bead count resulting in a beading $B^x$ at $n+\nicefrac23$.
Bead indices are counted inward from the outline (thick black).
Interpolation of locations in dots, interpolation of widths in dashes.
}
\label{beading_interpolation}
\end{figure}

@@

\begin{figure}
\centering
\setlength{\figheight}{.29\columnwidth}
\begin{subfigure}{0.14\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_beading.pdf}
\caption{Beadings}\label{trapezoid_beading_beading}
\end{subfigure}
\begin{subfigure}{0.5\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_propagated.pdf}
\caption{Single beading propagated to all nodes}\label{trapezoid_beading_propagated}
\end{subfigure}
\begin{subfigure}{0.34\columnwidth}\centering
\includegraphics[height=\figheight]{sources/method/trapezoid_beading_separate.pdf}
\caption{Separate beadings at either top node}\label{trapezoid_beading_separate}
\end{subfigure}
\caption{
Applying beadings to generate sites along trapezoids.
\subref{trapezoid_beading_beading} shows the locations $l_i$ and widths $w_i$ of two arbitrary different beadings.
\subref{trapezoid_beading_propagated} shows the application of $B^1$ to the various types of trapezoid.
\subref{trapezoid_beading_separate} shows how a trapezoid with a marked edge will have two different beadings assigned, which will generate their respective sites along the support edges.
No sites will be generated along marked edges.
Wide black lines are outline segments, marked nodes and edges in blue, the sites in yellow and green wavefronts of equidistant radial distance at $R = l_i$.
}
\label{site_placement}
\end{figure}

### 2019-08-29 5_generalization.tex
Tim: remove upper half of beadings B which was unused and fix some fomulae issues

\begin{definition}\label{beading_scheme_definition}
The beading scheme is configured by the following set of functions and constants:
\begin{align*}
\{
&q(d),
B(n, d),
t(n),
t_0(n),
\\
&\alpha_\text{max}, 
t_\text{beading}, 
d_\text{max}^\text{transition}, 
d_\text{max}^\text{unmarked}, 
d_\text{max}^\text{intersection},
d^\text{discretization}
 \}
\end{align*}
where, as introduced in previous section,
$q(d)$ the quantization operator,
$B(n,d)$ is the beading function consisting of $\left( W(n,d), L(n,d) \right)$,
$t(n)$ the transition length,
$t_0(n)$ the transition anchor position,
$\alpha_{\text{max}}$ is the limit bisector angle,
$t_\text{beading}$ is the beading conflict transition length,
$d_\text{max}^\text{unmarked}$ is the filter distance for unmarked regions,
$d_\text{max}^\text{transition}$ is the filter distance for transition anchors,
$d_\text{max}^\text{intersection}$ is the reduction ratio at 3-way intersections
and
$d^\text{discretization}$ is the discretization length in vertex-vertex VD edges and vertex-line VD edges.
%$W(n, d)$ and $L(n, d)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item Beadings are symmetric from the center: $W(n, d)_i = W(n, d)_{n-i-1}$ and $L(n, d)_i = d - L(n, d)_{n-i-1}$
%\item $W$ is symmetric: $W(n, d)_i = W(n, d)_{n-i-1}$
%\item $L$ is symmetric in $d$: $L(n, d)_i = d - L(n, d)_{n-i-1}$
\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, d)_n}{\partial d} \leq 1$
\end{enumerate}

@@

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
L(n,d)_i = 
\begin{cases}
-\frac12 W(n,d)_i + \sum_{j=0}^i W(n,d)_j & \text{ if } i < \frac12 (n -1) \\
d/2 & \text{ if } i =  \frac12 (n -1) \\
d - W(n,d)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\\
\begin{array}{rlrl}
t_\text{beading} &= w^* 
&
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}
\\
t(n) &= w^*
&
d_\text{max}^\text{unmarked} &= w^*
\\
t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right)
&
d^\text{discretization} &= \SI{0.2}{\milli\meter}
\\
\alpha_\text{max} &= \SI{135}{\degree} 
&
d_\text{max}^\text{intersection} &= \SI{75}{\percent}
\end{array}
%\end{align*}
%\begin{align*}
\end{align*}

The toolpath locations $L$ ensure 
that the beads don't overlap,
that beads are extruded from the center of where they end up
and that the symmetry restrictions are met.
The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $2 R(v) = n w^*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.

%\fboxsep=10mm%padding thickness
\begin{figure}%\centering
\setlength{\figwidth}{.2\textwidth}
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
\captionsetup[subfigure]{justification=justified,singlelinecheck=false}
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
%\frame{
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
W(n,d)_i &= w^* \text{ for all } i 
%\\
%L(n,d)_i &= w^* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}
\caption{Uniform scheme}\label{formula_uniform}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
q(d) &=
\begin{cases}
1 & \text{ if } d < w^* \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,d)_i &= 
\begin{cases}
d & \text{ if } n = 1 \\
w^* & \text{ otherwise } \\
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } n = 1 \\
%w^* / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}
\caption{Outer bead}\label{formula_outer_bead}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
\alpha_\text{max} &= \SI{0}{\degree} \\
q(d) &= C \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}
\caption{Constant bead count}\label{formula_constant_bead_count}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
W(n,d)_i &= d / n \text{ for all } i 
%\\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}
\caption{Evenly distributed}\label{formula_evenly_distributed}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
t(n) &= \frac12 w^* \\
%q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
q(d) &= q^-(d) +
\begin{cases}
-1 & \text{ if } q^-(d) w^* - d > w^* - r_\text{max} \\
1  & \text{ if }  q^-(d) w^* - d < w^* - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,d)_i &= 
\begin{cases}
d - (n-1) w^* &\text{ if } i = \frac12 (n-1) \\
w^* &\text{ otherwise }
\end{cases}
%\\
%L(n,d)_i &= 
%\begin{cases}
%d / 2 & \text{ if } i = \frac12 (n-1) \\
%w^* \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}
\caption{Centered}\label{formula_centered}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
E(n,d) &= d - n w^* \\
W(n,d)_i &= w^* + E(n,d) \frac{M(n,d)_i}{\sum_{j=0}^{n-1} M(n,d)_j} \text{ for all } i \\
%L(n,d)_i &= d / n (i + \frac12) \text{ for all } i < \frac12 n
M(n,d)_i &= \max(0, 1 - \frac{1}{N^2} (i - (n-1)/2)^2 )
\end{align*}
\caption{Inward distributed}\label{formula_inward_distributed}
\end{subfigure}
}
\caption{
Beading schemes.
}
\label{beading_schemes}
\end{figure}

@@

\paragraph{Inward distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w^* + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $M(n.d)$, which defines the portion of the discrepancy to distribute to each bead.
%\paragraph{Inward distributed}
For example, we can choose an $M$ which distributes the discrepancy over the innermost beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w^*$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
%Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.
See \cref{formula_inward_distributed}.

@@

\paragraph{Widening}
Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
We can simply override
\begin{align*}
W'(n,d)_1 &=
\begin{cases}
\max \left( w_\text{nozzle}  ,  W(n,d)_1 \right) & \text{ if } n = 1 \\
W(n,d)_1 & \text{ otherwise}
\end{cases}
\end{align*}

>>>>

\begin{definition}\label{beading_scheme_definition}
The beading scheme is configured by the following set of functions and constants:
\begin{align*}
\{
&q(d),
B(n, r),
t(n),
t_0(n),
\\
&\alpha_\text{max}, 
t_\text{beading}, 
d_\text{max}^\text{transition}, 
d_\text{max}^\text{unmarked}, 
d_\text{max}^\text{intersection},
d^\text{discretization}
 \}
\end{align*}
where, as introduced in previous section,
$q(d)$ the quantization operator,
$B(n,r)$ is the beading function consisting of $\left( W(n,r), L(n,r) \right)$,
$t(n)$ the transition length,
$t_0(n)$ the transition anchor position,
$\alpha_{\text{max}}$ is the limit bisector angle,
$t_\text{beading}$ is the beading conflict transition length,
$d_\text{max}^\text{unmarked}$ is the filter distance for unmarked regions,
$d_\text{max}^\text{transition}$ is the filter distance for transition anchors,
$d_\text{max}^\text{intersection}$ is the reduction ratio at 3-way intersections
and
$d^\text{discretization}$ is the discretization length in vertex-vertex VD edges and vertex-line VD edges.
%$W(n, r)$ and $L(n, r)$ give the sequence of bead widths $\left\{ w_i \right\}$ and radial locations $\left\{ l_i \right\}$, respectively.
\end{definition}

The following restrictions hold:
\begin{enumerate}
\item Transitions shouldn't overlap each other: $t_1(n) + t_0(n+1) < \frac{ q^{-1}(n + 1) - q^{-1}(n) }{ \cos \nicefrac12 \alpha_\text{max}}$ for each $n \in \mathbb{N}$ (see \cref{transition_placement})
\item An odd beading should produce an odd single toolpath exactly in the center: $B(n, r)_{\lfloor n/2 \rfloor} = r$ in case $n$ is odd
\item For toolpaths to be smooth and continuous we require that $W_n$ is monotonic and continuous at each bead index $n$ for constant bead count $c$: $0 \leq \frac{\partial W(c, r)_n}{\partial r} \leq 1$
\end{enumerate}

@@

A beading scheme is defined as a set of some particular variables and functions (\cref{beading_scheme_definition}).
Our beading schemes are based on a preferred width $w^* = \SI{0.4}{\milli\meter}$, which is equal to the diameter of the printing nozzle.
Most of the beading schemes we introduce share a common ground:
\begin{align*}
L(n,r)_i = 
\begin{cases}
-\frac12 W(n,r)_i + \sum_{j=0}^i W(n,r)_j & \text{ if } i < \frac12 (n -1) \\
r & \text{ if } i =  \frac12 (n -1) \\
%d - W(n,r)_{n-1-i} & \text{ otherwise }\\
\end{cases}
\\
\begin{array}{rlrl}
t_\text{beading} &= w^* 
&
d_\text{max}^\text{transition} &= \SI{1}{\milli\meter}
\\
t(n) &= w^*
&
d_\text{max}^\text{unmarked} &= w^*
\\
t_0(n) &=  t(n) \left( q^{-1}(n) / w^*  - n \right)
&
d^\text{discretization} &= \SI{0.2}{\milli\meter}
\\
\alpha_\text{max} &= \SI{135}{\degree} 
&
d_\text{max}^\text{intersection} &= \SI{75}{\percent}
\end{array}
%\end{align*}
%\begin{align*}
\end{align*}

The toolpath locations $L$ ensure 
that the beads don't overlap,
that beads are extruded from the center of where they end up
and that the symmetry restrictions are met.
The transition anchor position $t_0$ ensures that the transitions never overlap with the locations $v$ where $R(v) = \nicefrac12 n w^*$ for $n \in \mathbb{N}$.
The transition length $t$ ensures that the center beads don't overlap with the innermost transitioning beads, while keeping the amount of underfill low and keeping the toolpath smooth.
The limit bisector angle $\alpha_\text{max}$ ensures that we don't employ transitioning in shallow wedge regions, which would result in a lot of short odd single bead polylines, which would break up the semi-continuous nature of polygonal extrusion paths.

%\fboxsep=10mm%padding thickness
\begin{figure}%\centering
\setlength{\figwidth}{.2\textwidth}
\setlength{\abovedisplayskip}{0pt}
\setlength{\belowdisplayskip}{0pt}
\captionsetup[subfigure]{justification=justified,singlelinecheck=false}
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
%\frame{
\begin{align*}
\alpha_\text{max} &= \SI{180}{\degree} \\
q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
W(n,r)_i &= w^* \text{ for all } i 
%\\
%L(n,r)_i &= w^* \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}
\caption{Uniform scheme}\label{formula_uniform}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
q(d) &=
\begin{cases}
1 & \text{ if } d < w^* \\
2 & \text{ otherwise } \\
\end{cases}
 \\
W(n,r)_i &= 
\begin{cases}
2r & \text{ if } n = 1 \\
w^* & \text{ otherwise } \\
\end{cases}
%\\
%L(n,r)_i &= 
%\begin{cases}
%2r / 2 & \text{ if } n = 1 \\
%w^* / 2 & \text{ otherwise } \\
%\end{cases}
\end{align*}
\caption{Outer bead}\label{formula_outer_bead}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
\alpha_\text{max} &= \SI{0}{\degree} \\
q(d) &= C \\
W(n,r)_i &= 2 r / n \text{ for all } i 
%\\
%L(n,r)_i &= 2r / n \left(i + \frac12 \right) \text{ for all } i < \frac12 n
\end{align*}
\caption{Constant bead count}\label{formula_constant_bead_count}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
W(n,r)_i &= 2 r / n \text{ for all } i 
%\\
%L(n,r)_i &= 2r / n (i + \frac12) \text{ for all } i < \frac12 n
\end{align*}
\caption{Evenly distributed}\label{formula_evenly_distributed}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
t(n) &= \frac12 w^* \\
%q^-(d) &= 2 \left\lfloor \frac{d}{ 2w^*} + \frac12 \right\rfloor \\
q(d) &= q^-(d) +
\begin{cases}
-1 & \text{ if } q^-(d) w^* - d > w^* - r_\text{max} \\
1  & \text{ if }  q^-(d) w^* - d < w^* - r_\text{min} \\
0 & \text{ otherwise}
\end{cases}
\\
W(n,r)_i &= 
\begin{cases}
2 r - (n-1) w^* &\text{ if } i = \frac12 (n-1) \\
w^* &\text{ otherwise }
\end{cases}
%\\
%L(n,r)_i &= 
%\begin{cases}
%2r / 2 & \text{ if } i = \frac12 (n-1) \\
%w^* \left(i + \frac12 \right) & \text{ otherwise }
%\end{cases}
\end{align*}
\caption{Centered}\label{formula_centered}
\end{subfigure}
}
%
%
\fbox{
\begin{subfigure}[b]{\figwidth}\centering
\begin{align*}
q(d) &= \left\lfloor \frac{d}{ w^*} + \frac12 \right\rfloor \\
E(n,r) &= 2r - n w^* \\
W(n,r)_i &= w^* + E(n,r) \frac{\omega(n,r)_i}{\sum_{j=0}^{n-1} \omega(n,r)_j} \text{ for all } i \\
%L(n,r)_i &= 2r / n (i + \frac12) \text{ for all } i < \frac12 n
\omega(n,r)_i &= \max(0, 1 - N^{-2} (i - (n-1)/2)^2 )
\end{align*}
\caption{Inward distributed}\label{formula_inward_distributed}
\end{subfigure}
}
\caption{
Beading schemes.
}
\label{beading_schemes}
\end{figure}

@@

\paragraph{Inward distributed scheme}
The evenly distributed scheme can be conceptualized as calculating the total discrepancy $E$ between the actual feature diameter $d$ and the total preferred width $n w^*$, dividing the total discrepancy by the number of beads and setting the width of each bead to 
$w^* + E / n$.
However, depending on the application we might want a different distribution of widths.
We therefore supply a beading scheme which supports an arbitrary distribution of the discrepancy.
The distribution is determined by some weighing function $\omega(n,r)$, which defines the portion of the discrepancy to distribute to each bead.
%\paragraph{Inward distributed}
See \cref{formula_inward_distributed}.
For example, we can choose an $\omega$ which distributes the discrepancy over the innermost $N$ beads, and distribute most of it to the inner beads.
See \cref{distributed_comparison}.
That way we limit the region of impact of the distributed scheme to a central region and have the nominal bead width $w^*$ in regions farther away.
This limits the impact of transitioning regions so that transitions keep the toolpaths smooth farther away from the central regions. % and it forces most of the beads to have exactly the prefered width.
%Moreover, the bead widths equal the nominal bead width for large regions meaning that mechanical properties derived for prints using the uniform scheme will still hold approximately.

@@

\paragraph{Widening}
Complementary to any of these schemes we can enforce a minimum feature size at no extra cost in our framework.
Regions where the model is narrower than the nozzle size can be printed with a bead width larger than the model thickness.
We can simply override
\begin{align*}
W'(n,r)_0 &=
\begin{cases}
\max \left( w^*  ,  W(n,r)_0 \right) & \text{ if } n = 1 \\
W(n,r)_0 & \text{ otherwise}
\end{cases}
\end{align*}

### 2019-08-29 6_validation.tex
Tim: remove upper half of beadings B which was unused and fix some fomulae issues

We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$. The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.

>>>>

We evaluate the proposed framework and the various beading schemes on a set of different types of 3D models, ranging over various applications and various types of geometry. 
The data set is described in Appendix~\ref{dataset}.
We sliced all models in the data set and selected 300 random slices for analysis.
Toolpaths of these 300 outline shapes are generated using the uniform technique as implemented by Clipper~\cite{johnson2014clipper} -- a state-of-the-art polygon offset library, and by our framework using four beading schemes, i.e. the constant bead count scheme with a bead count of $C=4$, the centered, the evenly distributed, and the inward distributed beading scheme using $N=3$, all with a nominal bead widths of $w^*] = \SI{0.4}{\milli\meter}$. The tests were performed on a desktop PC equipped with an Intel Core i7-7500U CPU @ \SI{2.70}{\giga\hertz} (a single core is used) and \SI{16.3}{\giga\byte} memory.
